---
title: "CodeBook"
author: "Craig Parman"
date: "2/18/2015"
output:
  html_document:
    keep_md: yes
---


Code book for "tall_skiny_summary.txt"

#summary

This data table was created from the UCI HAR data set.  See the readme for download instructions and through description of the raw data.

The data in tall_skiny_summary.txt consists of the mean and standard deviation for all values of the test and training data sets.  Only column that we results of means and standard deviation were used . *(Yeah, that makes no sense, but that was what the instructions said)*  All proicessing steps are in run_analysis.R

#columns
There are 4 columns in the final table.


```{r}
t<-read.table("tall_skiny_summary.txt",header=TRUE)
print(names(t))
```

#Variables

##Subject

Meaning: Number assigned to test subject.

Values:  1 to 30, 876 observations for each.

##Activity
Meaning: Type of activity during data collection

Values:  6 values 
1. WALKING
2. WALKING_UPSTAIRS
3. WALKING_DOWNSTAIRS
4. SITTING
5. STANDING
6. LAYING

##Measure
Meaning:  The measurement and the type of summary statistic either mean or standard deviation. All values are in the form [raw measure].[initial summary]_statistic, where statistic is eith mean or std.

Value: 1 of the 146 values listed.
```{r} 
print(names(table(t$Measure)))

```

##Value
Meaning: value of the summary statistic calculated.

Value: These floating point values. Units were not specified in the original data. 
  
